troubleshooting

### 2024-04-27 README.Rmd
fixed to clear all devtools::check() warnings

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE
)
```

@@

### Loading the files ###
lfq_filename = "tests/protein-peptides-lfq.csv"
#file "protein-peptides.csv" exported from PEAKS identification
id_filename = "tests/protein-peptides-id.csv"

# Prepare the data for normalyzer analysis
prepared_data = prepare_peaks(lfq_filename,id_filename)

# saving to data folder in package for tests. Ignore when using on your own data
usethis::use_data(prepared_data,overwrite = TRUE)
```

@@

Before we normalyze data, we need to know what samples are in what groups. We can do that by defining a design matrix. 
```{r}
design_matrix = readr::read_csv("tests/design_matrix.csv")

@@

msp-ms uses the .... package to do normalization under the hood.

Now we can normalyze the data.
```{r}
normalyzed_data = normalyze(prepared_data,design_matrix)

@@

```{r}
design_matrix = readr::read_csv("tests/design_matrix.csv")
outliers = handle_outliers(normalyzed_data,design_matrix)

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = FALSE
)
```

@@

### Loading the files ###
lfq_filename = "tests/testdata/protein-peptides-lfq.csv"
#file "protein-peptides.csv" exported from PEAKS identification
id_filename = "tests/testdata/protein-peptides-id.csv"

# Prepare the data for normalyzer analysis
peaks_prepared_data = prepare_peaks(lfq_filename,id_filename)

# saving to data folder in package for tests. Ignore when using on your own data
usethis::use_data(peaks_prepared_data,overwrite = TRUE)
```

@@

Before we normalyze data, we need to know what samples are in what groups. We can do that by defining a design matrix. 
```{r}
design_matrix = readr::read_csv("tests/testdata/design_matrix.csv")

@@

msp-ms uses the normalyzede package to do normalization under the hood.

Now we can normalyze the data.
```{r}
normalyzed_data = normalyze(peaks_prepared_data,design_matrix)

@@

```{r}
design_matrix = readr::read_csv("tests/testdata/design_matrix.csv")
outliers = handle_outliers(normalyzed_data,design_matrix)
